### 2021-02-18 README.Rmd

[![](https://img.shields.io/badge/devel%20version-0.0.1.300-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
[![Build Status](https://travis-ci.com/c1au6i0/covid19census.svg?branch=master)](https://travis-ci.com/c1au6i0/covid19census)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)

>>>>

[![](https://img.shields.io/badge/devel%20version-0.0.1.400-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
[![Build Status](https://travis-ci.com/c1au6i0/covid19census.svg?branch=master)](https://travis-ci.com/c1au6i0/covid19census)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
